---
output: github_document
---

# An Explanation for This Repository's Name

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%",
  fig.align = "center"
)
```

[I got tired of the peer-review process](https://twitter.com/stevenvmiller/status/1229788167223398400) changing the names of my projects. When this happened, my repository names would no longer make sense. [I started creating nicknames for my projects](https://twitter.com/stevenvmiller/status/1229788168049676294) at the project's onset, using either the Ubuntu Name Generator or the Wu-Tang Name Generator. This led to the creation of an R package---`{codename}`---that would do this for me. This is what came out for this particular idea of mine.

```{r}
library(codename)

message(paste0("code name generated by {codename} v.", packageVersion("codename")))

all_types <- c("any", "gods", "ubuntu", "wu-tang")
options(warn = -1) # this is a long seed
for (i in all_types) {
  output <- codename(type = i, seed  = "Steve’s Methods Guide: A Book on Intermediate Methods That Will Assuredly Have a Better Name When I’m Done With It")
  print(output)
}
```

I liked "sky sheep" the best, so "sky sheep" it is.